---
title: "Question 1 instruction"
editor_options: 
  chunk_output_type: console
---

NOTE: you don't need to knit this file.

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

The following will start a new project called `kendalltau`. You might encounter

> New project 'kendalltau' is nested inside an existing project './', which is rarely a good idea.

And it is expected. Create anyway.

```{r, eval = FALSE}
library(devtools)
create_package("kendalltau")
```

After creating the package project, a new RStudio window should be opened.

The goal of this package is to provide an R function and an Rcpp function to compute the Kendall's $\tau$ correlction coefficient.

Suppose we have pairs $(x_i, y_i)$, $i=1,...,n$. The Kendall's Tau is defined as
$$
\tau = \frac{n_c - n_d}{\binom{n}{2}}
$$
where $n_c$ is the number of concordant pairs and $n_d$ is the number of discordant pairs.

Any pair of observations $(x_{i},y_{i})$ and $(x_{j},y_{j})$, where $i<j$, are said to be concordant if the sort order of $(x_{i},x_{j})$ and $(y_{i},y_{j})$ agrees: that is, if either both $x_{i}>x_{j}$ and $y_{i}>y_{j}$ holds or both $x_{i}<x_{j}$ and $y_{i}<y_{j}$; otherwise they are said to be discordant.

##### (a) In the package, create an R function `tau` in the package that computes the Kendall's Tau between `x` and `y`.

##### (b) In the package, create another function `fasttau` using Rcpp that computes the kendall's Tau.


You could pretty much follow the instructions in `https://r-pkgs.org/` chapter 2. However, please skip step 2.5 and 2.17 - we don't need them because the assignment Rproj is already managing the package Rproj.

You will need to do the followings.

- Implement the functions.
- Write documentations.
- Write simple tests using `testthat`.
  - check if your results are consistant with `cor.test(x, y, method = "kendall")`.
- Pass the test by running `devtools::check()` test (or use the "Test Package" button in the Build pane).
- Install the package with `devtools::install()` (or use the "Install and Restart" button in the Build pane).
- Do not forget to stage, commit and push your package at the end.
