---
title: "Question 2"
---


```{r, message = FALSE}
library(tidyverse)
```

Suppose we have two variables `x` and `y` and we want to calculate the correlations between them.
The observations are spread into 100 files (generated with the below code).

```{r, eval = FALSE}
dir.create("files", showWarnings = FALSE)
set.seed(141)
1:100 %>% walk(function(i) {
    dt <- tibble(x = rnorm(5000), y = rnorm(5000))
    write_csv(dt, file.path("files", sprintf("file%02d.csv", i)))
})
```

##### (a) Combine all files and compute the sample correlation between `x` and `y`.



Part (a) could be quite memory demanding because it requires to combine all files into one huge dataframe. An approximation of part (a) can be done by using map-reduce.


##### (b) Use `parLapply` to compute the (approximated) sample correlation between `x` and `y`.

Hint: you should read the data in the workers.



##### (c) Use `parLapplyLB` to compute the (approximated) sample correlation between `x` and `y`.



##### (e) Benchmark part (a) to part (c). Comment on the speeds.

