---
title: "Question 3"
---

##### (a) By using the function `fasttau` (or `tau`) developed in question 1, develop a classical bootstrap procedure to compute an arbitrary level confidence interval for the population Kendall's Tau between two variables.


```{r}
library(kendalltau)
#' Compute confidence interval for Kendall's Tau.
#' @param x a numeric vector
#' @param y a numeric vector
#' @param B integer, number of bootstrap samples
#' @param level numeric, between 0 and 1.
#' @return lower and upper bound of the confidence interval
tau_ci <- function(x, y, B = 10000, level = 0.95) {

}
```

```{r}
tau_ci(mtcars$mpg, mtcars$hp, level = 0.90)
tau_ci(mtcars$mpg, mtcars$hp, level = 0.95)
tau_ci(mtcars$mpg, mtcars$hp, level = 0.99)
```


##### (b) Compute a 95\% confidence interval for the population Kendull's Tau using the data in `data.csv`.




##### (c) For bivariate normal data, it is known that the population Kendull's Tau is

$$
\tau = \frac{2}{\pi} \text{arcsin}{\rho}
$$
where $\rho$ is the Pearson correlation.

Use this fact to construct a confidence interval for $\rho$ together with the result from part (b).

